---
title: "FLG 5161 Urban Environment"
output:
  html_document:
    df_print: paged
---
Data: Qualar - Cetesb

Dia: 2023-08-05

Poluentes: PM2.5

Marginal
Av. Embaixador Macedo Soares, 12889
Vila Leopoldina - São Paulo -
Centro de Treinamento do Comando de
Policiamento Rodoviário da Polícia Militar
23k 322013
7397977
COORD. UTM
(SIRGAS 2000)

Ibirapuera
Parque do Ibirapuera s/nº - setor 25
Prq. Ibirapuera - São Paulo
23k 330545
7389978
COORD. UTM
(SIRGAS 2000)


Try executing this chunk by clicking the *Run* button within the chunk or by placing your cursor inside it and pressing *Ctrl+Shift+Enter*. 

```{r}
ibirapuera = read.csv("data/ibirapuera.csv", sep=";", encoding="iso-8859-1", stringsAsFactors=FALSE, fileEncoding = "iso-8859-1")
marginal = read.csv("data/marginal.csv", sep=";", encoding="iso-8859-1", stringsAsFactors=FALSE, fileEncoding = "iso-8859-1")
data = cbind(hora = substring(ibirapuera$Hora,1,2), ibirapuera = ibirapuera$Média.Horária, marginal = marginal$Média.Horária)
data = as.data.frame(data)
```


```{r}
library(ggplot2)
library(dplyr)

ggplot() +
  ggtitle("PM2.5 concentration in August 5, 2023 for Parque do Ibirapuera \n and Marginal Cebolão") +
  geom_line(data = data, aes(x=hora, y=marginal, group = 1), color = "red") +
  geom_line(data = data, aes(x=hora, y=ibirapuera, group = 1), color = "blue") +
  geom_point(data = data, aes(x=hora, y=marginal, group = 1), shape=21, color="black", fill="red", size=2) +
  geom_point(data = data, aes(x=hora, y=ibirapuera, group = 1), shape=21, color="black", fill="blue", size=2) +
  xlab('Hour in August 5, 2023 (last saturday)') +
  ylab('Microgram per metre cubic') +
  geom_text(aes(x = 11, y = 20, label = "Marginal (Cebolão)"),color = "red") + 
  geom_text(aes(x = 5, y = 15, label = "Parque do Ibirapuera"),color = "blue")
 
ggsave("/tmp/graph.png")

```

